Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: rephrase research questions
AB-review: Remove unncessary paragraph in intro

	\item Does combining feature sets have an substantial effect on predictive performance?

@@

\noindent \ac{RF}, \ac{SVM} and extreme gradient boosting were fitted on six feature sets using different feature selection methods.
Bayesian Optimization, also known as model-based optimization, was used for hyperparameter tuning and optimization of the number of features.
By merging all optimization steps into a single step, multiple optimization stages, which may introduce bias cause long model fitting times, were avoided.
A spatial \ac{CV} approach on the plot level was used to account for spatial autocorrelation in the data.

>>>>

	\item Can predictive performance be substantially improved by combining feature sets?

@@
